% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
\usepackage{linespacing_fix} % Disable extra space before next section
\usepackage{cite}
\usepackage[colorlinks,linkcolor=blue]{hyperref}
\usepackage{fontawesome} % Ensure this package is loaded for FontAwesome icons

\begin{document}
\pagenumbering{gobble} % Suppress displaying page number

\name{Fuliang Xu}
\vspace{2ex}
\contactInfo{\href{mailto:trevorxu@berkeley.edu}{trevorxu@berkeley.edu}}{(+1) 628-306-8780}{}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of California, Berkeley}}{Aug. 2018 -- Dec. 2024}
\textit{Bachelor of Art} in Computer Science

\section{\faSitemap\ Work Experience}

\datedsubsection{\textbf{YumChina | Shanghai, China}}{Jan. 2021 -- May 2024}
\begin{itemize}
  \item Developed and maintained ETL pipelines for KFC’s sales and transactional data, ensuring accurate data transformation and seamless integration with downstream applications.
  \item Implemented scalable Python scripts for data cleaning and transformation, significantly improving data quality and reliability.
  \item Utilized SQL to design and manage databases in Hive, enabling efficient storage and querying of large datasets.
  \item Led the development of a daily sales prediction model for over 5,000 KFC stores across China using ensemble learning, improving forecast accuracy by 20\% compared to the previous system.
  \item Detected and addressed supply chain inefficiencies by analyzing seasonal patterns, reducing national supply underflow by 30\% through improved logistics planning.
  \item Built regression models to analyze pricing sensitivity for Pizza Hut products, providing actionable insights for pricing strategy.
  \item Collaborated with cross-functional teams on business analysis projects, including monitoring user engagement and assessing the impact of marketing initiatives.
\end{itemize}

\datedsubsection{\textbf{upSWOT | Berkeley, CA}}{Sep. 2019 -- Dec. 2020}
\begin{itemize}
  \item Worked on the eCommerce team of four interns and a mentor with a goal of using data to observe and test CRM and analyze how a client company could better maximize its profit.
  \item Tracked issues, needs, and preferences of large companies to help lenders and insurers cross-sell more and in a highly automated way.
  \item Utilized SQL to design and manage databases in Hive, enabling efficient storage and querying of large datasets.
  \item Performed EDA and data cleaning on client datasets.
  \item Used NumPy to help organize the tables extracted from the API.
\end{itemize}

\datedsubsection{\textbf{Coconut Island | Shanghai, China}}{June 2019 -- Aug. 2019}
\begin{itemize}
  \item In-game Pop-up and Website Development: Designed, developed, and maintained in-game pop-up web pages and multiple game-related websites using HTML, CSS, and JavaScript, ensuring consistent performance across devices and screen sizes.
  \item User Experience and Performance Optimization: Enhanced player experience through the implementation of animations, responsive designs, and performance optimization techniques like code splitting and lazy loading for fast, smooth interactions.
  \item Cross-team Collaboration and A/B Testing: Worked closely with game designers, back-end developers, and the marketing team to seamlessly integrate pop-ups within the game, conducted A/B testing, and optimized user engagement and conversion rates.
  \item Backend Integration with Python Django: Leveraged Python Django to integrate and manage user data, providing personalized content and efficient data collection for enhanced user experience.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Proficient in Python, Java, HTML/CSS, JavaScript, Shell, SQL.
  \item Experienced with Git, QEMU, Docker, AWS, GCP, Jenkins, Vivado, Unreal Engine 4, Hive, Pandas.
  \item Strong knowledge of Linux, RISC-V, Spring Boot, Kafka, Gin, gRPC, React.js, Vue.js, Redis, MongoDB, SPDK.
\end{itemize}

\pagebreak

\end{document}